---
output: pdf_document
---

ECON 121 FINAL EXAM - FALL 2022

Name: 

8 December 2022

I hereby declare I wrote my own written answers and my own code and did not copy from anyone else. I understand that copying some else's answer can result in negative infinity points for both parties. 

Question 1

```{r}

# code here

```

Question 2

Written answer here.

Question 3

```{r}

# code here

```

Question 4

Written answer here.

Question 5

```{r}

# code here

```

Question 6

Written answer here.

Question 7

```{r}

# code here

```

Question 8

Written answer here.

Question 9

```{r}

# code here

```

Question 10

Written answer here.

Question 11

Written answer here.

Question 12

Written answer here.

Question 13

Written answer here.

Question 14

```{r}

# code here

```

Question 15

```{r}

# code here

```

Question 16

Written answer here.

Question 17

```{r}

# code here

```

Question 18

Written answer here.

Question 19

Written answer here.

Question 20

```{r}

# code here

```
